Psyc 601 Multivariate Statistics Project

### 2013-08-26 writeups/proposal/proposal.tex
foo
Former-commit-id: cf9f679145fba44530b496828036ab51f634c185 [formerly ff187ee8c940177eebc7d76b4aa289850694082d]
Former-commit-id: 4ba43c415cd639a943f13f5969bee025c0f2908d

Several other models have taken a tweet-centered approach to hashtag prediction, where suggested hashtags are collected from hashtags used from similar tweets.
\textcites{Li2011, Zangerle2011, Kywe2012} all store a content vector for each tweet, and then compute a word co-occurence-based similarity score between a composed tweet and the rest of the tweets in the database.
\textcites{Zangerle2011, Kwye2012} use the Apache Lucine infrastructure to compute the similarity score, while \textcite{Li2011} uses a custom similarity score derived from the WordNet database to compute similarites.
Regardless of the method to compute the similarity between tweets, each method collects the hashtags used from a set of the most similar tweets, then ranks the set, and presents the top 5-10 hashtags to the user.

@@

\textcite{kwye2012} also customized their tag predictino model to the user's past hashtag use, and was one of the first to do so when developing a hashtag-prediction model for Twitter.
The set of recommended hashtags was the union of hashtags used in similar tweets and hashtags used by similar users.
This was done by storing a content vector of hshtag use for each user (user-centered approach) alongside the content vectors of hashtag use for each tweet (tweet-centered approach).
To generate recommended hashtags, the model would return the top-ranked hashtags from the hashtags used in 0-50 similar tweets and 0-4 similar users.
Prediction accuracy improved when the model generated recommendations based on hashtags in both similar tweets and the top few similar users compared to basing recommendations on similar tweets alone.

>>>>

Several other models have taken a tweet-centered approach to hashtag prediction, where suggested hashtags are collected from hashtags used from similar tweets.
\textcites{Li2011, Zangerle2011, Kywe2012} all store a content vector for each tweet, and then compute a word co-occurence-based similarity score between a composed tweet and the rest of the tweets in the database.
\textcites{Zangerle2011, Kywe2012} use the Apache Lucine infrastructure to compute the similarity score, while \textcite{Li2011} uses a custom similarity score derived from the WordNet database to compute similarites.
Regardless of the method to compute the similarity between tweets, each method collects the hashtags used from a set of the most similar tweets, then ranks the set, and presents the top 5-10 hashtags to the user.

@@

\textcite{Kywe2012} also customized their tag predictino model to the user's past hashtag use, and was one of the first to do so when developing a hashtag-prediction model for Twitter.
The set of recommended hashtags was the union of hashtags used in similar tweets and hashtags used by similar users.
This was done by storing a content vector of hshtag use for each user (user-centered approach) alongside the content vectors of hashtag use for each tweet (tweet-centered approach).
To generate recommended hashtags, the model would return the top-ranked hashtags from the hashtags used in 0-50 similar tweets and 0-4 similar users.
Prediction accuracy improved when the model generated recommendations based on hashtags in both similar tweets and the top few similar users compared to basing recommendations on similar tweets alone.
